Parametric controls on vegetation responses to biogeochemical forcing in the CLM5

### 2019-07-03 main_revision.tex
Updates from Overleaf

The impact of \emph{slatop} on fertilization was different at every site (figs. \ref{GPP_CN}, figures \ref{LAI_CN}). For MET, \emph{slatop} was the most important control over N responses, with higher values allowing a greater LAI/GPP feedback in response to the N fertilization. At NWR, the opposite behaviour was found, with high SLA reducing the impact of N in cases where the pre-fertilization LAI meant that a saturating response of GPP was found. At HVF, higher values of \emph{slatop} slightly reduced both CO$_{2}$ and N fertilization for the same reason (although the range of variation at HVF is only 5\% between the highest and lowest values, as opposed to 40\% at NWR). 
\emph{froot\_leaf} had contrasting impacts at different sites.  At MET,  where low values increased the CO$_{2}$ fertilization, probably due to the increased drought stress under those conditions. At HVF, low \emph{froot\_leaf} decreased both CO$_{2}$ and N fertilization on account of higher initial LAI, mirroring the respnse to \emph{slatop}.

@@

At all site, higher $N_{costs}$ increases the responsiveness of the system to N, and to a lesser extent CO$_{2}$.

parameterization primarily impacts the respiration expended on N uptake and the availability of carbon for tissue growth thus, its impact is greatest for LAI (Figure \ref{LAI CO2 and N respones 2001}). At Caxiuan\~a, Niwot and Harvard forest, high  $N_{costs}$ resulted in stronger LAI responses to N fertilization, since these cases had higher N limitation in the first instance (Figure \ref{btran state}).  These high $N_{costs}$ scenarios also showed a slight increase in the CO$_{2}$ fertilization response, perhaps since their high N limitation was alleviated by extra assimilated carbon.   Low values of $N_{costs}$ were associated with low CO$_{2}$ responses (and vice versa) in particular at Caxiuana and Harvard Forest, which can be interpreted as a reflection of the lower C expenditure on N uptake in the control simulations.  While nitrogen uptake costs are important to the fertilization responses, they do not affect the total amount of N in the system, and therefore appeared to play a secondary role to the amount of N fixation available.

The fraction of N fixers (\emph{frac\_fixers}) has a particularly dominant role over the model response to step changes in N and to CO$_{2}$. For GPP and LAI, all sites displayed a 'trade-off', whereby high N fixer systems responded strongly to CO$_{2}$ but not N, and low fixer systems responded strongly to N but not CO$_{2}$ (Figure \ref{GPP CO2 and N respones 2001}, \ref{LAI CO2 and N respones 2001}).  For NPP, N deposition responses were muted at Metolius, and reversed in sign at Caxiuan\~a, where the low N fixer cases had a very negative (-8\%) NPP response (despite a +7.6\% GPP response), on account of the model increasing the N content of the leaves (and thus respiration rates) by up to 10\% in the lowest N cost case (SI Figure 6). Nonetheless, given the lower N uptake costs in the fertilized N experiment, leaf area was substantially increased (up to 14\%) in these cases too.  At Niwot Ridge the changing fixation capacity had no impact on the response of GPP to N fixation, despite its influence on LAI, suggesting that water limitation was a greater constraint on total GPP than leaf area.  At Metolius, again the changing fixation capacity had no impact on the response of GPP to N deposition (Figure \ref{GPP CO2 and N respones 2001}) but in this case, it had no impact on LAI either. Only \emph{slatop} and \emph{stem\_leaf} had large impacts on N fertilization at this site, suggesting fundamental metabolic limitations to canopy carbon economics (e.g. a short growing season) that render only higher LAI simulations sensitive to fertilization.

The impact of target \emph{leafcn} on fertilization responses was not particularly dominant (recalling that this was a significant control over the system state at all sites), an exception being Niwot Ridge, where low values of \emph{leafcn} had very strong to CO$_{2}$ fertilization (the strongest response at this site for GPP). These cases suffered from high water limitation, given their high $N\_{leaf}$ values and high gas exchange fluxes (Figure \ref{btran state}) and thus CO$_{2}$ fertilization alleviates this problem. At Caxiuan\~a, high \emph{leafcn} cases had stronger responses to N fertilization, but responses to N fertilization were low at this site in general.

>>>>

The impact of \emph{slatop} on fertilization was different at every site (figs. \ref{GPP_CN}, figures \ref{LAI_CN}). For MET, \emph{slatop} was the most important control over N responses, with higher values allowing a greater LAI/GPP feedback in response to the N fertilization. At NWR, the opposite behaviour was found, with high SLA reducing the impact of N in cases where the pre-fertilization LAI meant that a saturating response of GPP was found. At HVF, higher values of \emph{slatop} slightly reduced both CO$_{2}$ and N fertilization for the same reason (although the range of variation at HVF is only 5\% between the highest and lowest values, as opposed to 40\% at NWR).

\emph{froot\_leaf} had contrasting impacts at different sites.  At MET,  where low values increased the CO$_{2}$ fertilization, probably due to the increased drought stress under those conditions. At HVF, low \emph{froot\_leaf} decreased both CO$_{2}$ and N fertilization on account of higher initial LAI, mirroring the respnse to \emph{slatop}.

@@

At CAX, NWT and HVF, higher $N_{costs}$ increases the responsiveness of the system to N, and to a lesser extent CO$_{2}$.  The magnitude of the impact on N fertilization appeared to be related to the extent of N limitation in the pre-fertilization state (Figure \ref{btran state}).   Very low values of $N_{costs}$ appeared to reduce the responsiveness of the system to CO$_{2}$ fertilization, particularly at CAX and HVF.

The fraction of N fixers (\emph{frac\_fixers}) has a particularly dominant role over the model response to step changes in N and to CO$_{2}$. For GPP and LAI, all sites displayed a 'trade-off', whereby high \emph{frac\_fixers} systems responded strongly to CO$_{2}$ but not N, and low \emph{frac\_fixers} systems responded strongly to N but not CO$_{2}$ (Figure \ref{GPP_CN}, \ref{LAI_CN}).   At MET,  the changing fixation capacity had no impact on the response of GPP or LAI to N fertilization.  Only \emph{slatop} and \emph{stem\_leaf} had large impacts on N fertilization for this site (which had the smallest PNU in the first instance), suggesting fundamental metabolic limitations to carbon economics and growth (e.g. a short growing season).

The impact of \emph{leafcn} on fertilization responses was not as dominant a control over fertilization responses as it was over the system state. The primary impacts were at, an exception being Niwot Ridge, where low values of \emph{leafcn} had a low response to N fertilization These cases suffered from high water limitation, given their high $N\_{leaf}$ values and high gas exchange fluxes (Figure \ref{btran state}) and thus CO$_{2}$ fertilization alleviates this problem. At CAX, high \emph{leafcn} cases had stronger responses to N fertilization, reflecting the higher PNU in those cases prior to fertilizaion.
